Clean spectral data

### 2020-10-31 R/clean_spectral_data.Rmd
trying to get paper to knit
but it depends on a lot of things, not working yet
working on methods text

---
title: "Clean spectral data"
author: "Victoria Scholl"
date: "09/10/2020"
output: html_document
---

@@

Write spectra to csv file. 
```{r}
write_csv(x = filtered_spectra,
          path = here::here("data", "cleaned_spectra.csv"))
```

>>>>

---
title: "Clean spectral data"
output: html_document
---

@@

Write spectra to csv file. 
```{r}
write_csv(x = filtered_spectra,
          path = here::here("analysis", "data", "derived_data", "cleaned_spectra.csv"))
```
